---
title: "Redmond et al 2021 - Demultiplexing"
output: html_notebook
---

#Setup
```{r}
library(AUCell)
library(GSEABase)
library(Seurat)
library(shiny)
library(viridis)
library(scales)
library(scico)
library(ggplot2)
library(patchwork)
library(sctransform)
library(tidyr)
```

#Reading the Cellranger output and Creating a Seurat Object
```{r}
svz_matrix <- Read10X(
  data.dir = c("/data4/svz_10x/wholecell/data/pipestance/g1/outs/filtered_feature_bc_matrix",
               "/data4/svz_10x/wholecell/data/pipestance/g2/outs/filtered_feature_bc_matrix"),
  unique.features = TRUE,
  strip.suffix = FALSE
)

exp <- CreateSeuratObject(counts = svz_matrix$`Gene Expression`)
exp[['Protein']] <- CreateAssayObject(counts = svz_matrix$`Antibody Capture`)

exp
```

```{r}
#Barcodes used: A3(TGAGACCT), A4(GCACACGC), A5(AGAGAGAG), A6 (TCACAGCA)
seurat.cells <- names(experiment$orig.ident)
cell.id.vec <- seurat.cells
multi.ref <- c("TGAGACCT", "GCACACGC", "AGAGAGAG", "TCACAGCA")
```


#1. Demultiplexing
##On terminal:
```{bash}
#Loading the original FastQ files was not possible due their huge size (R2 is 27gb, while the preprocessing is optimized for files under 2gb). We have to downsample our barcode fastqfiles to 100M reads:

gunzip TGACCAAT_S5_L001_R2_001.fastq.gz
gunzip TGACCAAT_S5_L001_R1_001.fastq.gz
seqtk sample -s100 TGACCAAT_S5_L001_R2_001.fastq 100000000 > TGACCAAT_S5_L001_R2_001_subsampled.fastq
seqtk sample -s100 TGACCAAT_S5_L001_R1_001.fastq 100000000 > TGACCAAT_S5_L001_R1_001_subsampled.fastq
gzip TGACCAAT_S5_L001_R2_001_subsampled.fastq
gzip TGACCAAT_S5_L001_R1_001_subsampled.fastq

gunzip ACAGTGAT_S6_L001_R1_001.fastq.gz
gunzip ACAGTGAT_S6_L001_R2_001.fastq.gz
seqtk sample -s100 ACAGTGAT_S6_L001_R1_001.fastq 100000000 > ACAGTGAT_S6_L001_R1_001_subsampled.fastq
seqtk sample -s100 ACAGTGAT_S6_L001_R2_001.fastq 100000000 > ACAGTGAT_S6_L001_R2_001_subsampled.fastq
gzip ACAGTGAT_S6_L001_R2_001_subsampled.fastq
gzip ACAGTGAT_S6_L001_R1_001_subsampled.fastq
```


##Loading FastQ files
```{r}
#tgacaat - B1
#acagtgat - B2

#B1:
readTable.b1 <- MULTIseq.preProcess(R1 = "/data4/svz_10x/wholecell/data/fastq/subsampled/TGACCAAT_S5_L001_R1_001_subsampled.fastq.gz", R2 = "/data4/svz_10x/wholecell/data/fastq/subsampled/TGACCAAT_S5_L001_R2_001_subsampled.fastq.gz", cellIDs = cell.id.vec)
save(readTable.b1, file= "readTable.b1.Rdata")

#B2:
readTable.b2 <- MULTIseq.preProcess(R1 = "/data4/svz_10x/wholecell/data/fastq/subsampled/ACAGTGAT_S6_L001_R1_001_subsampled.fastq.gz", R2 = "/data4/svz_10x/wholecell/data/fastq/subsampled/ACAGTGAT_S6_L001_R2_001_subsampled.fastq.gz", cellIDs = b2.cells.fixed)
save(readTable.b2, file= "readTable.b2.Rdata")
```

##Determining cell IDs in B1 and B2
```{r}
#This is a convoluted and non optimal way to determine the cell ids in B1 and B2. Instead, it should be determined using a filtering function to detect the b2 prefix "2_" as a regular expression and then separate the B1 and B2 ids. I am leaving this code here as this is how I originally determined B1 and B2 cells for future reference.

#all cells
all.cells <- names(experiment$orig.ident)

#B1:
b1.cells <- unique(readTable %>% select(Cell))
b1.cells <- as.vector(b1.cells[,1])
save(b1.cells, file = "b1.cells.Rdata")

#B2:
b2.cells <- all.cells[!(all.cells %in% b1.cells)]
save(b2.cells, file = "b2.cells.Rdata")

#b1.cells IDS:
b1.cells[1] #"ATTCCTACATACTGAC"
nchar(b1.cells[1]) #16 characters

b2.cells[1] #"2_AAACCCAAGAGCTGAC"
nchar(b2.cells[1]) #18 characters

#we have to remove the 2_ prefix of b2 ids in order to align reads:
b2.cells.fixed <- sub("2_", "", b2.cells)#b2.fixed was the reference used to align in the previous chunk 
```

##Checking the number of unique cells
```{r}
unique(readTable.b1 %>% select(Cell)) #18,028
unique(readTable.b2 %>% select(Cell)) #16,979
unique(readTable %>% select(Cell)) #18,046: the number of cells in G1. This is when we realized B2 wasn't being read.
```

## Perform MULTI-seq sample barcode alignment
```{r}
bar.table.b1 <- MULTIseq.align(readTable.b1, b1.cells, multi.ref)
save(bar.table.b1, file = "bar.table.b1.Rdata")

bar.table.b2 <- MULTIseq.align(readTable.b2, b2.cells.fixed, multi.ref)
save(bar.table.b2, file = "bar.table.b2.Rdata")
```

##Visual inspection in the barcode space
```{r}
#B1
bar.tsne.b1 <- barTSNE(bar.table.b1 [,1:4]) 
save(bar.tsne.b1, file="bar.tsne.b1.Rdata")

pdf("b1.bc.check.pdf")
for (i in 3:ncol(bar.tsne.b1)) {
    g <- ggplot(bar.tsne.b1, aes(x = TSNE1, y = TSNE2, color = bar.tsne.b1[,i])) +
    geom_point() +
    scale_color_gradient(low = "black", high = "red") +
    ggtitle(colnames(bar.tsne.b1)[i]) +
    theme(legend.position = "none") 
    print(g)
}
dev.off()

#B2
bar.tsne.b2 <- barTSNE(bar.table.b2 [,1:4]) 
save(bar.tsne.b2, file="bar.tsne.b2.Rdata")

pdf("b2.bc.check.pdf")
for (i in 3:ncol(bar.tsne.b2)) {
    g <- ggplot(bar.tsne.b2, aes(x = TSNE1, y = TSNE2, color = bar.tsne.b2[,i])) +
    geom_point() +
    scale_color_gradient(low = "black", high = "red") +
    ggtitle(colnames(bar.tsne.b2)[i]) +
    theme(legend.position = "none") 
    print(g)
}
dev.off()
```

## Round 1 / B1
```{r}
## Perform Quantile Sweep
bar.table.b1.full <- bar.table.b1[,1:4]
good.bars <- paste("Bar",1:4,sep="")  # Selecting all 4 barcodes
bar.table.b1 <- bar.table.b1.full[, good.bars]  # Remove missing bars and summary columns
bar.table_sweep.list.b1 <- list()
n <- 0
for (q in seq(0.01, 0.99, by=0.02)) {
  print(q)
  n <- n + 1
  bar.table_sweep.list.b1[[n]] <- classifyCells(bar.table.b1, q=q)
  names(bar.table_sweep.list.b1)[n] <- paste("q=",q,sep="")
}

## Identify ideal inter-maxima quantile to set barcode-specific thresholds
threshold.results.b1.1 <- findThresh(call.list=bar.table_sweep.list.b1)
ggplot(data=threshold.results.b1.1$res, aes(x=q, y=Proportion, color=Subset)) + geom_line() +
  geom_vline(xintercept=threshold.results.b1.1$extrema, lty=2) + scale_color_manual(values=c("red","black","blue"))

# Finalize round 1 classifications, remove negative cells
b1.round1.calls <- classifyCells(bar.table.b1, q=findQ(threshold.results.b1.1$res, threshold.results.b1.1$extrema))
b1.neg.cells <- names(b1.round1.calls)[which(b1.round1.calls == "Negative")]
bar.table.b1 <- bar.table.b1[-which(rownames(bar.table.b1) %in% b1.neg.cells), ]
```

## Round 1 / B2 
```{r}
## Perform Quantile Sweep
bar.table.b2.full <- bar.table.b2[,1:4]
good.bars <- paste("Bar",1:4,sep="")  # Selecting all 4 barcodes
bar.table.b2 <- bar.table.b2.full[, good.bars]  # Remove missing bars and summary columns
bar.table_sweep.list.b2 <- list()
n <- 0
for (q in seq(0.01, 0.99, by=0.02)) {
  print(q)
  n <- n + 1
  bar.table_sweep.list.b2[[n]] <- classifyCells(bar.table.b2, q=q)
  names(bar.table_sweep.list.b2)[n] <- paste("q=",q,sep="")
}

## Identify ideal inter-maxima quantile to set barcode-specific thresholds
threshold.results.b2.1 <- findThresh(call.list=bar.table_sweep.list.b2)
ggplot(data=threshold.results.b2.1$res, aes(x=q, y=Proportion, color=Subset)) + geom_line() +
  geom_vline(xintercept=threshold.results.b2.1$extrema, lty=2) + scale_color_manual(values=c("red","black","blue"))

# Finalize round 1 classifications, remove negative cells
b2.round1.calls <- classifyCells(bar.table.b2, q=findQ(threshold.results.b2.1$res, threshold.results.b2.1$extrema))
b2.neg.cells <- names(b2.round1.calls)[which(b2.round1.calls == "Negative")]
bar.table.b2 <- bar.table.b2[-which(rownames(bar.table.b2) %in% b2.neg.cells), ]
```

## Round 2 /B1
```{r}
bar.table_sweep.list.b1 <- list()
n <- 0
for (q in seq(0.01, 0.99, by=0.02)) {
  print(q)
  n <- n + 1
  bar.table_sweep.list.b1[[n]] <- classifyCells(bar.table.b1, q=q)
  names(bar.table_sweep.list.b1)[n] <- paste("q=",q,sep="")
}

threshold.results.b1.2 <- findThresh(call.list=bar.table_sweep.list.b1)
b1.round2.calls <- classifyCells(bar.table.b1, q=findQ(threshold.results.b1.2$res, threshold.results.b1.2$extrema))
b1.neg.cells <- c(b1.neg.cells, names(b1.round2.calls)[which(b1.round2.calls == "Negative")])

ggplot(data=threshold.results.b1.2$res, aes(x=q, y=Proportion, color=Subset)) + geom_line() +
  geom_vline(xintercept=threshold.results.b1.2$extrema, lty=2) + scale_color_manual(values=c("red","black","blue"))
```

## Round 2 /B2
```{r}
bar.table_sweep.list.b2 <- list()
n <- 0
for (q in seq(0.01, 0.99, by=0.02)) {
  print(q)
  n <- n + 1
  bar.table_sweep.list.b2[[n]] <- classifyCells(bar.table.b2, q=q)
  names(bar.table_sweep.list.b2)[n] <- paste("q=",q,sep="")
}

threshold.results.b2.2 <- findThresh(call.list=bar.table_sweep.list.b2)
b2.round2.calls <- classifyCells(bar.table.b2, q=findQ(threshold.results.b2.2$res, threshold.results.b2.2$extrema))
b2.neg.cells <- c(b2.neg.cells, names(b2.round2.calls)[which(b2.round2.calls == "Negative")])

ggplot(data=threshold.results.b2.2$res, aes(x=q, y=Proportion, color=Subset)) + geom_line() +
  geom_vline(xintercept=threshold.results.b2.2$extrema, lty=2) + scale_color_manual(values=c("red","black","blue"))
```

## Repeat until all no negative cells remain (usually 3 rounds)...
## Round 3 /B1 
```{r}
bar.table_sweep.list.b1 <- list()
n <- 0
for (q in seq(0.01, 0.99, by=0.02)) {
  print(q)
  n <- n + 1
  bar.table_sweep.list.b1[[n]] <- classifyCells(bar.table.b1, q=q)
  names(bar.table_sweep.list.b1)[n] <- paste("q=",q,sep="")
}

threshold.results.b1.3 <- findThresh(call.list=bar.table_sweep.list.b1)
b1.round3.calls <- classifyCells(bar.table.b1, q=findQ(threshold.results.b1.3$res, threshold.results.b1.3$extrema))
b1.neg.cells <- c(b1.neg.cells, names(b1.round3.calls)[which(b1.round3.calls == "Negative")])

ggplot(data=threshold.results.b1.3$res, aes(x=q, y=Proportion, color=Subset)) + geom_line() +
  geom_vline(xintercept=threshold.results.b1.3$extrema, lty=2) + scale_color_manual(values=c("red","black","blue"))

## Repeat until all no negative cells remain (usually 3 rounds)...
b1.final.calls <- c(b1.round3.calls, rep("Negative",length(b1.neg.cells)))
names(b1.final.calls) <- c(names(b1.round3.calls),b1.neg.cells)
save(b1.final.calls, file="b1.final.calls.Rdata")
```

## Round 3 /B2
```{r}
bar.table_sweep.list.b2 <- list()
n <- 0
for (q in seq(0.01, 0.99, by=0.02)) {
  print(q)
  n <- n + 1
  bar.table_sweep.list.b2[[n]] <- classifyCells(bar.table.b2, q=q)
  names(bar.table_sweep.list.b2)[n] <- paste("q=",q,sep="")
}

threshold.results.b2.3 <- findThresh(call.list=bar.table_sweep.list.b2)
b2.round3.calls <- classifyCells(bar.table.b2, q=findQ(threshold.results.b2.3$res, threshold.results.b2.3$extrema))
b2.neg.cells <- c(b2.neg.cells, names(b2.round3.calls)[which(b2.round3.calls == "Negative")])

ggplot(data=threshold.results.b2.3$res, aes(x=q, y=Proportion, color=Subset)) + geom_line() +
  geom_vline(xintercept=threshold.results.b2.3$extrema, lty=2) + scale_color_manual(values=c("red","black","blue"))

## Repeat until all no negative cells remain (usually 3 rounds)...
b2.final.calls <- c(b2.round3.calls, rep("Negative",length(b2.neg.cells)))
names(b2.final.calls) <- c(names(b2.round3.calls),b2.neg.cells)
save(b2.final.calls, file="b2.final.calls.Rdata")
```

## Add back the prefix to cell IDs in B2 data to incorporate in 
```{r}
names(b2.final.calls) <- paste0("2_", names(b2.final.calls))
final.calls <- c(b1.final.calls, b2.final.calls)

```

##Saving
```{r}
experiment.deMPx <- experiment
experiment.deMPx@meta.data[,"MULTI"] <- "Unknown"
experiment.deMPx@meta.data[names(final.calls), "MULTI"] <- final.calls
save(experiment.deMPx, file = paste0("WC_sctransformed_demultiplexed_",Sys.Date(),".Rdata"))
````